Global Distribution of Unintended Pregnancies and Contraceptive Usage

### 2024-04-01 code/analysis-code/statistical-analysis.qmd
Statistical Analysis Updates
I added MAE as another performance metric and completed cross-validation for the two best models. I graphed the testing and training predictions using the MLR model. I updated the manuscript methods and results for part 4.

---
title: "Statistical Analysis"
author: "Taylor Glass and Arlyn Santiago"
date: "03/12/24"
output: html_document
---
## Load necessary packages
```{r}
#| message: false
library(dplyr) # for basic syntax
library(broom) #for cleaning up output from lm()
library(here) #for data loading/saving
library(tidymodels) # for model building 
library(yardstick) # for finding performance metrics 
library(rsample) #for splitting the data into testing/training
```

@@

# explore the pairwise comparisons
tidy(tukey_result)
```
ANOVA results show that the region variable is statistically significantly associated with the outcome variable given the p-value less than 0.001. The Tukey HSD test revealed the largest differences in the outcome between the Oceania region and Latin America/the Caribbean, Europe, and Asia. The relationships between Oceania and Europe and Latin America/the Caribbean are statistically significant with p-values less than 0.0001. Oceania is clearly experiencing the lowest percentage of unintended pregnancies among short acting reversible method users.  The lowest difference in outcome between regions is between Asia and Africa, but this is not a statistically significant association. Two statistically significant differences in the outcome exist between Latin America/the Caribbean and Europe with Africa, which shows that Africa is experiencing higher levels of the outcome.

@@

### Assessing correlation between predictors
There are some variables that are intuitively correlated, which means they should not be included in the same model. We want to explore those correlations before building our multivariate linear regression model. 
```{r}
# find correlation coefficients 
cor(mydata$pct_currentlymarried, mydata$pct_nevermarried)
cor(mydata$rate_matdeaths, mydata$rate_matdeaths_upreg)
cor(mydata$rate_matdeaths, mydata$rate_matdeaths_abs)
cor(mydata$rate_matdeaths_upreg, mydata$rate_matdeaths_abs)
```
The percent of currently married women and the percent of never married women have a correlation coefficient of -0.8588, so these two variables are highly correlated. The total rate of maternal deaths and rate of maternal deaths due to unintended pregnancies is the most highly correlated pair with a coefficient of 0.8904. The correlation between total rate of maternal deaths and rate of maternal deaths due to abortion is slightly lower with a coefficient of 0.8023. The two variables with the least correlation out of these four pairs are rate of maternal deaths due to unintended pregnancies and rate of maternal deaths due to abortion with a coefficient of 0.6486. Based on these associations, we will only include the percent of currently married women in the multivariate model because it has a slightly larger effect on the outcome with a more significant p-value in its single predictor model compared to the percent of never married women predictor. We will include both the rate of maternal deaths due to unintended pregnancies and rate of maternal deaths due to abortion beccause the total rate of maternal deaths is so highly correlated with each of these variables.

@@

## Assessing Model Performance
It is important to consider appropriate metrics to measure model performance. We will use RMSE at this point to compare 3 models: one with the number of women using short acting reversible contraception predictor, one using the percent never married predictor, and one using the rate of maternal deaths due to abortion predictor. We chose these predictors because they have the strongest associations with the outcomes based on the single linear regression models shown above. 
```{r}
# set seed for reproducibility 
set.seed(2468)

@@

# find RMSE to determine model fit
rmse1 <- rmse(popdata, truth = pct_upreg_sarc, estimate = .pred)

@@

# find RMSE to determine model fit
rmse2 <- rmse(marrieddata, truth = pct_upreg_sarc, estimate = .pred)

@@

# find RMSE to determine model fit
rmse3 <- rmse(matdeath_absdata, truth = pct_upreg_sarc, estimate = .pred)

@@

# find RMSE to determine model fit
rmse4 <- rmse(nulldata, truth = pct_upreg_sarc, estimate = .pred)

# compare the metrics 
print(rmse1)
print(rmse2)
print(rmse3)
print(rmse4)
```

The RMSE metric favors the model with the total number of women using short acting reversible contraception methods based on a low RMSE value of 5.143319. The model with the percentage of women currently married performs worse with an RMSE value of 10.17591. The same conclusion can be drawn for the model with the rate of maternal mortality due to abortions predictor only, given the RMSE value of 10.14128. The null model has an RMSE value of 9.842267, so all models should have an RMSE lower than this to be considered useful.

It is important to determine if our model with the region predictor performs well because the main question to be answered by this analysis depends on this predictor. Since region is a categorical variable, we cannot evaluate the RMSE performance metric.  
```{r}
# set seed for reproducibility 
set.seed(2468)

@@

# find RMSE to determine model fit
rmse5 <- rmse(regiondata, truth = pct_upreg_sarc, estimate = .pred)
print(rmse5)
```

The results of this RMSE value are disappointing because 18.11857 is much larger than the null model's RMSE of 9.842267. However, this issue could possibly be explained by the fact that Africa has the most significant differences in our outcome compared to the other regions. We will still include this predictor in our multivariate regression model based on the significant Tukey conclusions and the large differences in outcome displayed in our exploratory data analysis results.

@@

# find RMSE to determine model fit
rmse6 <- rmse(matdeathalldata, truth = pct_upreg_sarc, estimate = .pred)
print(rmse6)

@@

# find RMSE to determine model fit
rmse7 <- rmse(matdeath_upregdata, truth = pct_upreg_sarc, estimate = .pred)
print(rmse7)

@@

# find RMSE to determine model fit
rmse8 <- rmse(totalratedata, truth = pct_upreg_sarc, estimate = .pred)
print(rmse8)

# display RMSE values for each model
print(rmse6) #rate of maternal mortality predictor only
print(rmse7) #rate of maternal mortality due to unintended pregnancy predictor only
print(rmse3) #rate of maternal mortality due to abortion predictor only
print(rmse8) #all 3 rates of maternal mortality predictors together 
```
The RMSE values shows that the three single predictor models perform worse than the null model, which is not ideal. The model with all 3 maternal morality rate predictors performs exactly the same as the null model, which makes sense because the coefficients estimating the effect of each predictor on the outcome are so small.

@@

# find RMSE to determine model fit
rmse9 <- rmse(alldata, truth = pct_upreg_sarc, estimate = .pred)
print(rmse9)
```
As expected, this model performs better than the single predictor models with the lowest RMSE score of 4.209.

## Cross-Validation to Assess Model Performance
While the RMSE performance is a good place to start for evaluating model performance, we need to determine how well the model performs on data it has not seen before to determine its usefulness. We will use the cross-validation process to do this. The first step is to split the data into testing and training portions. 
```{r}
# set seed for reproducibility
set.seed(2468)

@@

We will only cross-validate the multivariate regression model `lmfit8` because it performs the best in terms of RMSE. 
```{r}

```

>>>>

---
title: "Statistical Analysis"
author: "Taylor Glass and Arlyn Santiago"
date: "03/12/24"
output: html_document
---
## Load necessary packages
```{r}
#| message: false
library(dplyr) # for basic syntax
library(broom) #for cleaning up output from lm()
library(here) #for data loading/saving
library(tidymodels) # for model building 
library(yardstick) # for finding performance metrics 
library(rsample) #for splitting the data into testing/training
library(knitr) # to create performance metric tables 
library(parsnip) # to create a workflow for cross-validation
```

@@

# explore the pairwise comparisons
tidy(tukey_result)

# save fit results table  
table_file13 = here("results", "tables", "resulttable13.rds")
saveRDS(tukey_result, file = table_file13)
```
ANOVA results show that the region variable is statistically significantly associated with the outcome variable given the p-value less than 0.001. The Tukey HSD test revealed the largest differences in the outcome between the Oceania region and Latin America/the Caribbean, Europe, and Asia. The relationships between Oceania and Europe and Latin America/the Caribbean are statistically significant with p-values less than 0.0001. Oceania is clearly experiencing the lowest percentage of unintended pregnancies among short acting reversible method users.  The lowest difference in outcome between regions is between Asia and Africa, but this is not a statistically significant association. Two statistically significant differences in the outcome exist between Latin America/the Caribbean and Europe with Africa, which shows that Africa is experiencing higher levels of the outcome.

@@

### Assessing correlation between predictors
There are some variables that are intuitively correlated, which means they should not be included in the same model. We want to explore those correlations before building our multivariate linear regression model. 
```{r}
# find correlation coefficients 
cor(mydata$pct_currentlymarried, mydata$pct_nevermarried)
cor(mydata$rate_matdeaths, mydata$rate_matdeaths_upreg)
cor(mydata$rate_matdeaths, mydata$rate_matdeaths_abs)
cor(mydata$rate_matdeaths_upreg, mydata$rate_matdeaths_abs)
```
The percent of currently married women and the percent of never married women have a correlation coefficient of -0.8588, so these two variables are highly correlated. The total rate of maternal deaths and rate of maternal deaths due to unintended pregnancies is the most highly correlated pair with a coefficient of 0.8904. The correlation between total rate of maternal deaths and rate of maternal deaths due to abortion is slightly lower with a coefficient of 0.8023. The two variables with the least correlation out of these four pairs are rate of maternal deaths due to unintended pregnancies and rate of maternal deaths due to abortion with a coefficient of 0.6486. Based on these associations, we will only include the percent of currently married women in the multivariate model because it has a slightly larger effect on the outcome with a more significant p-value in its single predictor model compared to the percent of never married women predictor. We will include both the rate of maternal deaths due to unintended pregnancies and rate of maternal deaths due to abortion because the total rate of maternal deaths is so highly correlated with each of these variables.

@@

## Assessing Model Performance
It is important to consider appropriate metrics to measure model performance. We will use RMSE and MAE at this point to compare 3 models: one with the number of women using short acting reversible contraception predictor, one using the percent never married predictor, and one using the rate of maternal deaths due to abortion predictor. We chose these predictors because they have the strongest associations with the outcomes based on the single linear regression models shown above. We chose these performance metrics because they are commonly used for linear regression models like the ones we have created. RMSE provides an average magnitude of the error in the predictors, and MAE provides an average absolute difference between the predicted and actual values. We include both metrics to increase the validity of our results. 
```{r}
# set seed for reproducibility 
set.seed(2468)

@@

# find performance metrics to determine model fit
rmse1 <- rmse(popdata, truth = pct_upreg_sarc, estimate = .pred)
mae1 <- mae(popdata, truth = pct_upreg_sarc, estimate = .pred)

@@

# find performance metrics to determine model fit
rmse2 <- rmse(marrieddata, truth = pct_upreg_sarc, estimate = .pred)
mae2 <- mae(marrieddata, truth = pct_upreg_sarc, estimate = .pred)

@@

# find performance metrics to determine model fit
rmse3 <- rmse(matdeath_absdata, truth = pct_upreg_sarc, estimate = .pred)
mae3 <- mae(matdeath_absdata, truth = pct_upreg_sarc, estimate = .pred)

@@

# find performance metrics to determine model fit
rmse4 <- rmse(nulldata, truth = pct_upreg_sarc, estimate = .pred)
mae4 <- mae(matdeath_absdata, truth = pct_upreg_sarc, estimate = .pred)

# create a matrix with RMSE and MAE values
results <- as.table(matrix(c(rmse1$.estimate, mae1$.estimate, rmse2$.estimate, mae2$.estimate, rmse3$.estimate, mae3$.estimate,
                             rmse4$.estimate, mae4$.estimate), nrow = 4, ncol = 2, byrow = TRUE))

# add column names
colnames(results) <- c("RMSE", "MAE")

# add row names
rownames(results) <- c("Model 1-Population Size Using SARCs", "Model 2-Currently Married", 
                             "Model 3-Rate of Maternal Deaths(Abortion)", "Model 4-Null")

# print the table
kable(results)

# save performance metrics results table  
table_file11 = here("results", "tables", "resulttable11.rds")
saveRDS(results, file = table_file11)
```

Both metrics favor the model with the total number of women using short acting reversible contraception methods based on the lowest RMSE value of 5.143319 and lowest MAE value of 3.953767. The model with the percentage of women currently married performs worse with an RMSE value of 10.17591 and MAE value of 8.107884. The same conclusion can be drawn for the model with the rate of maternal mortality due to abortions predictor only, given the RMSE value of 10.14128 and MAE value of 8.21687. The null model has an RMSE value of 9.842267 and MAE of 8.21687, so all models should have performance metrics lower than these values to be considered useful.

It is important to determine if our model with the region predictor performs well because the main question to be answered by this analysis depends on this predictor. 
```{r}
# set seed for reproducibility 
set.seed(2468)

@@

# find performance metrics to determine model fit
rmse5 <- rmse(regiondata, truth = pct_upreg_sarc, estimate = .pred)
mae5 <- mae(regiondata, truth = pct_upreg_sarc, estimate = .pred)
print(rmse5)
print(mae5)
```

The results of these performance metrics are disappointing because 18.11857 is much larger than the null model's RMSE of 9.842267 and 14.66513 is also larger than the null model's MAE. However, this issue could possibly be explained by the fact that Africa has the most significant differences in our outcome compared to the other regions. We will still include this predictor in our multivariate regression model based on the significant Tukey conclusions and the large differences in outcome displayed in our exploratory data analysis results.

@@

# find performance metrics to determine model fit
rmse6 <- rmse(matdeathalldata, truth = pct_upreg_sarc, estimate = .pred)
mae6 <- mae(matdeathalldata, truth = pct_upreg_sarc, estimate = .pred)

@@

# find performance metrics to determine model fit
rmse7 <- rmse(matdeath_upregdata, truth = pct_upreg_sarc, estimate = .pred)
mae7 <- mae(matdeathalldata, truth = pct_upreg_sarc, estimate = .pred)

@@

# find performance metrics to determine model fit
rmse8 <- rmse(totalratedata, truth = pct_upreg_sarc, estimate = .pred)
mae8 <- mae(matdeathalldata, truth = pct_upreg_sarc, estimate = .pred)

# create a matrix with RMSE and MAE values
results2 <- as.table(matrix(c(rmse6$.estimate, mae6$.estimate, rmse7$.estimate, mae7$.estimate, rmse3$.estimate, mae3$.estimate,
                              rmse8$.estimate, mae8$.estimate, rmse4$.estimate, mae4$.estimate), nrow = 5, ncol = 2, byrow = TRUE))

# add column names
colnames(results2) <- c("RMSE", "MAE")

# add row names
rownames(results2) <- c("Maternal Morality Model", "Maternal Mortality due to Unintended Pregnancies Model", 
                        "Maternal Mortality due to Abortion Model", "All 3 Maternal Mortality Predictors Model", "Null Model")

# print the table
kable(results2)

# save performance metrics results table  
table_file12 = here("results", "tables", "resulttable12.rds")
saveRDS(results2, file = table_file12)

```
The performance metrics show that the three single predictor models perform worse than the null model, which is not ideal. The model with all 3 maternal morality rate predictors performs exactly the same as the null model, which makes sense because the coefficients estimating the effect of each predictor on the outcome are so small. There is more variation in RMSE values compared to MAE values, but the conclusions are the same.

@@

# find performance metrics to determine model fit
rmse9 <- rmse(alldata, truth = pct_upreg_sarc, estimate = .pred)
mae9 <- mae(alldata, truth = pct_upreg_sarc, estimate = .pred)
print(rmse9)
print(mae9)
```
As expected, this model performs better than the single predictor models with the lowest RMSE score of 4.361363 and lowest MAE score of 3.386193.

## Cross-Validation to Assess Model Performance
While the RMSE and MAE performance metrics are a good place to start for evaluating model performance, we need to determine how well the model performs on data it has not seen before to determine its usefulness. We will use the cross-validation process to do this. The first step is to split the data into testing and training portions. 
```{r}
# set seed for reproducibility
set.seed(2468)

@@

We will only cross-validate the single predictor model with the highest performance, `lmfit1`, with the total population size using short acting reversible contraception and the  multivariate regression model,`lmfit8`, because it performs the best in terms of RMSE and MAE. Our dataset is relatively small with only 132 observations, so we will use 5 folds for the cross-validation process.  
```{r}
# set seed for reproducibility
set.seed(2468)

# create 10 folds
folds <- vfold_cv(train_data, v=5)

# define the model specification
lm_spec <- linear_reg() %>% 
  set_engine("lm")

# initialize a workflow and fit it to 'lmfit1'
my_workflow <- workflow() %>%
  add_model(lm_spec) %>% 
  add_formula(pct_upreg_sarc ~ sarc_standard) %>% #specify the formula since we are not using a recipe
  fit(data = train_data)

# resample the model 
my_resample <- my_workflow %>% 
                fit_resamples(folds)

# initialize a workflow and fit it to 'lmfit8'
my_workflow2 <- workflow() %>%
  add_model(lm_spec) %>% 
  add_formula(pct_upreg_sarc ~ sarc_standard + region + pct_currentlymarried + rate_matdeaths_upreg + rate_matdeaths_abs) %>% #specify the formula since we are not using a recipe
  fit(data = train_data)

# resample the model 
my_resample2 <- my_workflow2 %>% 
                fit_resamples(folds)

# collect the metrics from both models
collect_metrics(my_resample)
collect_metrics(my_resample2)
```
The cross-validated results lead to the same conclusion: the multiple linear regression model with 5 predictors performs better. The RMSE value for the single predictor model with `sarc_standard` is 4.822226, which is lower the the first RMSE value of 5.143319. While the RMSE value for the multiple linear regression model is slightly higher than the first time it was calculated, it is still slightly lower at 4.405716. Additionally, the standard error the multiple linear regression model is 0.2768, which is lower than the standard error for the single predictor model of 0.3528. This means there is higher variance in the single predictor model. The R-squared value of 0.8206 for the multiple linear regression model is higher than 0.7861 for the single predictor model, which means the multiple linear regression model accounts for more of the variability in the data. Overall, the multiple linear regression model performs better.

Since we have concluded that the model with all 5 predictors performs the best, we will use this model to make predictions for the test data. We will create a graph to show how well the model performed on the training and testing data. 
```{r}
# set seed for reproducibility
set.seed(2468)

# create predictions using MLR model with the test data
testpred <- predict(my_workflow2, new_data = test_data) %>% 
                  select(.pred)

# create predictions using MLR model with training data
trainpred <- predict(my_workflow2, new_data = train_data) %>% 
                  select(.pred)

# create data frame with the observed values predicted values from model 2
plotdata <- data.frame(
  observed = c(train_data$pct_upreg_sarc), 
  training_model2 = c(trainpred$.pred), 
  test_model2 = c(testpred$.pred),
  model = rep(c("Observed", "Training Model", "Testing Model"), each = nrow(train_data))) # add label indicating the model

# create a visual representation with 2 sets of predicted and observed values 
ggplot(plotdata, aes(x = observed)) +
  geom_point(aes(y = training_model2, color = "training model"), shape = 3) +
  geom_point(aes(y = test_model2, color = "testing model"), shape = 3) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "black") + #add the 45 degree line
  xlim(0, 50) + #limit the x-axis values
  ylim(0, 50) + #limit the y-axis values
  labs(x = "Observed Values", y = "Predicted Values", title = "Comparing Training and Testing Data on MLR Model")
```
The training model predictions, shown in teal, hover pretty closely around the expected relationship between the outcome and the 5 predictors, which is depicted as the 45 degree line. The testing model predictions, shown in coral, are much more extreme than the training model predictions because they are farther from the 45 degree line. While there is some overlap between the two sets of predictions, it is likely that our model is overfitting the data.

### 2024-04-01 products/manuscript/Manuscript.qmd
Statistical Analysis Updates
I added another model with a combination of predictors and found more RMSE values to compare models. I found correlations between predictors and adjusted the multivariate model accordingly.
Statistical Analysis Updates
I added MAE as another performance metric and completed cross-validation for the two best models. I graphed the testing and training predictions using the MLR model. I updated the manuscript methods and results for part 4.

1) Is there a significant difference in the percentage of unintended pregnancies among short acting reversible contraception users among countries?

@@

Step three is the statistical analysis and model fitting portion found in the statistical-analysis.qmd file in the code > analysis-code folder. We explore the single outcome `pct_upreg_sarc` based on 7 predictors with simple linear regression, total number of women using short acting reversible methods, region, percent of currently married women, percent of women who never married, total rate of maternal mortality, rate of maternal mortality by unintended pregnancy, and rate of maternal mortality by abortion. We also assess the performance of the models in this file. Result tables for each model are stored in the results > tables folder.

@@

## Statistical analysis
_Explain anything related to your statistical analyses._
We began with a simple linear regression model with each of the 7 predictor variables. We also included a multiple linear regression model with all 7 predictors. We included the RMSE for two of the models to begin exploring model fit.

@@

The second model we created used the region predictor, which revealed that the Latin America/the Caribbean region had the strongest relationship with the outcome variable followed closely by the Asia region. The Oceania region does not appear to have a strong effect on the outcome variable with the Europe region only showing a slightly larger association. These associations can be seen in @statistical-analysis2.
```{r}
#| label: statistical-analysis2
#| fig-cap: "Regional Predictor"
#| echo: FALSE
readRDS(here("results","tables", "resulttable2.rds")) 
```
We created one model with all 7 predictors using multiple linear regression. This model shows the strongest predictor is the number of women using short acting reversible contraception. The next strongest predictor is the European region followed by the Latin America/the Caribbean region and the Asia region, which is a shift from the model with the singular region predictor. The Oceania region now has a negative association with the outcome. Both of the marriage status predictors are associated with a decrease in the outcome. The coefficient estimates for the rate of maternal death due to unintended pregnancies and abortion both flipped from the single predictor models to show a positive association with the outcome. 
```{r}
#| label: basic-statistical-analysis
#| fig-cap: "Multiple Linear Regression with 7 Predictors"
#| echo: FALSE
readRDS(here("results","tables", "resulttable8.rds")) 
```
The full statistical analysis can be found in the statistical-analysis.qmd file in the code > analysis-code folder.

>>>>

1) Is there a significant difference in the percentage of unintended pregnancies among short acting reversible contraception users among region?

@@

Step three is the statistical analysis and model fitting portion found in the statistical-analysis.qmd file in the code > analysis-code folder. We explore the single outcome `pct_upreg_sarc` based on 7 predictors with simple linear regression, total number of women using short acting reversible methods, region, percent of currently married women, percent of women who never married, total rate of maternal mortality, rate of maternal mortality by unintended pregnancy, and rate of maternal mortality by abortion. We also explore the differences in the outcome between regions using an ANOVA test and Tukey's Honestly Significant Difference test for pairwise comparisons within ANOVA. Result tables for each model and test are stored in the results > tables folder.

Step four is to critically analyze the performance of our models to determine which one performs the best in predicting our outcome, which is also done in the statistical-analysis.qmd file in the code > analysis-code folder. We chose 2 performance metrics to find for each of our 9 models: Root Mean Square Error (RMSE) and Mean Absolute Error (MAE). We chose these performance metrics because they are commonly used for linear regression models like the ones we have created. RMSE provides an average magnitude of the error in the predictors, and MAE provides an average absolute difference between the predicted and actual values. We include both metrics to increase the validity of our results. Once we decided on the final model, we use cross-validation to determine how well it will perform on data it has not seen before.

@@

## Statistical analysis
_Explain anything related to your statistical analyses._
We began with a simple linear regression model with each of the 7 predictor variables to determine the association betwen each variable and the outcome. We explored the region variable further because our main goal is to understand the difference in outcome by region. We used ANOVA to determine the difference between regions, and we added Tukey's Honeslty Significant Difference test to examine pairwise associations. This led to discovering correlations between some of the predictors, which we examined through correlation coefficients. We tried out a combination of these correlated predictors in 2 different models to further examine the interactions. After considering which predictors are most impactful on our outcome, we narrowed the final predictors down to a list of 5. We included a multiple linear regression model with all 5 of these predictors. We used the RMSE and MAE performance metrics to evaluate all 9 models that we created to determine which one fit best. Lastly, we used cross-validation to determine how well our multiple linear regression model performs on data it has not seen before.

@@

The second model we created used the region predictor, which revealed that the Latin America/the Caribbean region had the strongest relationship with the outcome variable followed closely by the Asia region. The Oceania region does not appear to have a strong effect on the outcome variable with the Europe region only showing a slightly larger association. These associations can be seen in @statistical-analysis2.
```{r}
#| label: statistical-analysis2
#| fig-cap: "Regional Predictor"
#| echo: FALSE
readRDS(here("results","tables", "resulttable2.rds")) 
```
The Tukey HSD test for the region predictor, shown in @statistical-analysis3, revealed the largest differences in the outcome between the Oceania region and Latin America/the Caribbean, Europe, and Asia. The differences between Oceania and Europe and Latin America/the Caribbean are the largest. Oceania is clearly experiencing the lowest percentage of unintended pregnancies among short acting reversible method users. Two more significant differences in the outcome exist between Latin America/the Caribbean and Europe with Africa, which shows that Africa is experiencing higher levels of the outcome. 
```{r}
#| label: statistical-analysis3
#| fig-cap: "Tukey HSD Test Results"
#| echo: FALSE
readRDS(here("results","tables", "resulttable13.rds")) 
```

We created one model with all 5 predictors using multiple linear regression, shown in @statistcal-analysis4. This model shows the strongest predictor is the number of women using short acting reversible contraception. The next strongest predictor is the European region followed by the Latin America/the Caribbean region and the Asia region, which is a shift from the model with the singular region predictor. The Oceania region now has a negative association with the outcome. The currently married predictor is associated with a weak decrease in the outcome. The coefficient estimates for the rate of maternal death due to unintended pregnancies and abortion both show a very weak positive association with the outcome. 
```{r}
#| label: statistical-analysis4
#| fig-cap: "Multiple Linear Regression with 5 Predictors"
#| echo: FALSE
readRDS(here("results","tables", "resulttable8.rds")) 
```
The full statistical analysis can be found in the statistical-analysis.qmd file in the code > analysis-code folder.
